Democratizing Secure Two-Party Computation

### 2017-10-12 OaklandSubmission/ex.tex

Moreover, it is difficult to maintain the code in Figure~\ref{fig:ex-aby}.
For example, if the multiplication is changed to a bitwise-or then,
in the absence of \tool, an efficiency-conscious developer would need to  use boolean circuits everywhere and would be tasked with removing all arithmetic circuits and the interconversion gates (the cost of  conversion overweighs the gains of performing an arithmetic addition instead of a boolean addition). 
 With \tool, the developer needs to change only a single character (replace {\tt *} in Figure~\ref{fig:ex-sml} with {\tt |}) to achieve the same effect. 
On this example and other small examples, we have found that the compiler generated C++ code from a \tool implementation is as efficient as manually written C++ code. In particular, for $w^Tx>b$, the compiler automatically generates code that uses arithmetic circuits for dot product and inserts appropriate conversion gates. Finally, although this paper uses ABY for evaluation, the  compiler can be easily retargeted to generate code for other cryptography backends. In particular,
ABY implements two party computation (2PC), i.e., SMC between two parties
and this paper focuses on this setting.

The \tool compiler provides strong static guarantees. For example, a well typed
\tool program is guaranteed to execute to termination without errors. A \tool program cannot go into non-termination or dereference illegal memory, i.e., no buffer overflows or underflows can happen at run time. This guarantees are
much stronger than what are offered by production compilers such as {\tt gcc}.
The primary reason that we are able to achieve these guarantees is because
\tool has been designed to be verifiable and is backed by formal semantics. 
Furthermore, the compiler output is guaranteed to be a cryptographically secure
implementation of the functionality declared by the \tool code. 
Moreover, the \tool compiler also generates a C implementation that can be run natively on a single machine for functional testing.

>>>>

Moreover, it is difficult to maintain the code in Figure~\ref{fig:ex-aby}.
For example, if the multiplication is changed to a bitwise-or then,
in the absence of \tool, an efficiency-conscious developer would need to  use boolean circuits everywhere and would be tasked with removing all arithmetic circuits and the interconversion gates (the cost of  conversion overweighs the gains of performing an arithmetic addition instead of a boolean addition). 
 With \tool, the developer needs to change only a single character (replace {\tt *} in Figure~\ref{fig:ex-sml} with {\tt |}) to achieve the same effect. 
On this example and other small examples, we have found that the compiler generated C++ code from a \tool implementation is as efficient as manually written C++ code. In particular, for $w^Tx>b$, the compiler automatically generates code that uses arithmetic circuits for dot product and inserts appropriate conversion gates. Finally, although this paper uses ABY for evaluation, the  compiler can be easily retargeted to generate code for other cryptography backends.
\nc{I like the above point. Perhaps we can mention something like this earlier in the intro itself?}

The \tool compiler provides strong static guarantees. For example, a well typed
\tool program is guaranteed to execute to termination without errors. A \tool program cannot go into non-termination or dereference illegal memory, i.e., no buffer overflows or underflows can happen at run time. These guarantees are
much stronger than what are offered by production compilers such as {\tt gcc}.
The primary reason that we are able to achieve these guarantees is because
\tool has been designed to be verifiable and is backed by formal semantics. 
Furthermore, the compiler output is guaranteed to be a cryptographically secure
implementation of the functionality declared by the \tool code. 
Moreover, the \tool compiler also generates a C implementation that can be run natively on a single machine for functional testing.

### 2017-10-12 OaklandSubmission/intro.tex

\section{Introduction}
\label{sec:intro}
Today it is hard for developers to create secure implementations using cryptographic techniques.
Typical developers lack an understanding of cryptography protocols
and cannot be expected to implement them correctly without tool support.
In an ideal world, a developer declares the functionality to be implemented
in a general purpose programming language and an automatic tool takes care
of all the cryptography and generates a secure and efficient implementation  of the functionality. 
This paper provides a language-based solution to make
secure multiparty computation (SMC) accessible to the software developer community.

@@

Secure multi-party computation \cite{yao,gmw} (SMC) is a powerful cryptographic tool that allows a set of mutually distrusting parties to compute a joint function of their secret inputs. Examples of these include various machine learning prediction algorithm where one party holds the secret input such as a medical report and the other party holds the ML model for disease prediction. Since the introduction of SMC in 1980's, there has been a large body of work \cite{..} that has transformed SMC from a mere theoretical tool to something practically efficient/usable. Hence, there have been efforts to make SMC accessible to non-specialist programmers. To understand the state-of-the-art, let us consider the following toy example.

Suppose a developer wants to compute $w^Tx >0$ securely using SMC. With the current techniques, he has two options. He can code up the functionality in a programmer friendly domain-specific language such as \cite{lambdaps,wysteria,oblivm} that would automatically compile it to an SMC protocol. The downside is that all of these works build on a cryptographic back-end that is either entirely boolean \cite{yao,gmw} or entirely arithmetic \cite{homo}. The efficiency of the generated SMC protocol is hence, bounded by the possibility of efficiently representing the function in a form that is compatible with the cryptographic back-end used. For instance, over $\ell$-bit integers, multiplication requires a boolean circuit of size  $O(\ell^2)$. 
For better efficiency, we would like to evaluate $w^Tx$ using an Arithmetic circuit and the comparison using a boolean circuit.
In fact, most interesting functions require a mix of arithmetic and boolean computations.
To address this issue, recently Demmler et al. \cite{aby} gave a cryptographic protocol for SMC where the parties can mix arithmetic and boolean computations. \footnote{Need to note somewhere that many works combined HE and Yao. Look at ABY for references.}
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, using their system requires the programmer to be aware of complex trade-offs between arithmetic and boolean cryptographic schemes. In their framework, the programmer is required to write circuits consisting of  arithmetic and boolean gates along with appropriate conversion gates. In short, as is also mentioned by the authors themselves, the current system is not suitable to be used by non-specialist programmers. \divya{Change tone...}
Our work .....

@@

In this work, we develop and implement our framework \tool for secure computation that achieves generality, performance and programmer productivity. The programmer writes a high level C-like program (instead of a circuit) to describe the function to be computed. Our compiler automatically generates an SMC protocol using a mix of Arithmetic and Boolean compute. Our compiler is general and can work with any secure implementation of a mix of arithmetic and boolean computations. In our work, we focus on semi-honest secure two-party computation. We build on ABY \cite{aby} that provides the suitable cryptographic back-end in this setting. We provide a formal type system and prove correctness and security of our compiler. We evaluate our system on various benchmarks such as logistic regression and convolutional neural network (CNN) for MNIST data \cite{minionn}, naive bayes, decision trees from \cite{shafindss}. Evaluations show that protocols generated by our compiler match the performance of hand-crafted protocols in most cases (see \sectionref{sec:eval}). \divya{Below, we will  give an overview of \tool and describe our contributions in more detail.}

@@

We give a formal {\em type system} for our language and prove useful properties. We prove that if a program type checks in our language then it would run correctly, e.g., there would not be any array index out of bounds error. The programmer writes a single code describing the inputs from each party and the function to be computed. Our compiler automatically generates separate executables for the server and the client that can be executed in the distributed setting. We prove the {\em correctness} for this compilation, i.e., the outputs obtained in the distributed execution are identical to the stand-alone execution by a trusted third party. We formally reduce the {\em security} of our system to the security of the cryptographic back-end. For details on formal language, correctness and security theorems see \sectionref{ld}.

Another issue in adoption of SMC is difficulty in scaling to large programs. 
%In general, SMC implementations struggle in scaling to large programssize of memory on a system limits the largest compute inside the SMC and hence,. 
The reason being all SMC implementations use a circuit-like representation as an intermediate representation. Hence, the largest compute that can be done securely is upper-bounded by the largest circuit that can fit in memory on a machine.
To address this issue, we develop a technique called \emph{pipelining} that allows us to run aribitrarily large programs. At a high level, we break the original program into a sequence of small sub-programs and mask the intermediate outputs using secure secret sharing between the two parties. We appropriately append the share-reconstruction function to the beginning of the subsequent sub-program. Now, we execute each of these sub-programs sequentially in our framework. We provide details of pipelining and prove the correctness and security of this transformation in \sectionref{pipe}.

>>>>

\section{Introduction}
\label{sec:intro}
Today it is hard for developers to create secure implementations using cryptographic techniques.
Typical developers lack an understanding of cryptography protocols
and cannot be expected to implement them correctly without tool support.
In an ideal world, a developer declares the functionality to be implemented
in a general purpose programming language and an automatic tool takes care
of all the cryptography and generates a secure and efficient implementation  of the functionality. 
This paper provides a language-based solution to make
secure multiparty computation (SMC) accessible to the software developer community. \nc{Why do we call it SMC? A bit non-standard for crypto audiences isnt it?}

@@

Secure multi-party computation \cite{yao,gmw} (SMC) is a powerful cryptographic tool that allows a set of mutually distrusting parties to compute a joint function of their secret inputs. Examples of these include various machine learning prediction algorithm where one party holds the secret input such as a medical report and the other party holds the ML model for disease prediction. Since the introduction of SMC in 1980's, there has been a large body of work \cite{..} that has transformed SMC from a mere theoretical tool to something practically efficient and usable. Hence, there have been efforts to make SMC accessible to non-specialist programmers. To understand the state-of-the-art, let us consider the following toy example.

Suppose a developer wants to compute $w^Tx >0$ securely using SMC. With the current techniques, he has two options. \nc{The two options appear quite far apart in the text. Can we make bullet points maybe?} He can code up the functionality in a programmer friendly domain-specific language such as \cite{lambdaps,wysteria,oblivm} that would automatically compile it to an SMC protocol. The downside is that all of these works build on a cryptographic back-end that is either entirely boolean \cite{yao,gmw} or entirely arithmetic \cite{homo}. The efficiency of the generated SMC protocol is hence, bounded by the possibility of efficiently representing the function in a form that is compatible with the cryptographic back-end used. For instance, over $\ell$-bit integers, multiplication requires a boolean circuit of size  $O(\ell^2)$. 
For better efficiency, we would like to evaluate $w^Tx$ using an Arithmetic circuit and the comparison using a boolean circuit.
In fact, most interesting functions require a mix of arithmetic and boolean computations.
To address this issue, recently Demmler et al. \cite{aby} gave a cryptographic protocol for SMC where the parties can mix arithmetic and boolean computations. \footnote{Need to note somewhere that many works combined HE and Yao. Look at ABY for references.}
Hence, the second option is to write the functionality in the system developed in \cite{aby}.
However, using their system requires the programmer to be aware of complex trade-offs between arithmetic and boolean cryptographic schemes. In their framework, the programmer is required to write circuits consisting of  arithmetic and boolean gates along with appropriate conversion gates. In short, as is also mentioned by the authors themselves, the current system is not suitable to be used by non-specialist programmers. \nc{Also say that the programmer would need to know which functionality is better suited for arithmetic/boolean and also how to split the complete functionality into such parts.} \divya{Change tone...}
Our work .....
\nc{Should we also say here that a third option is to hire a cryptographer and build specific crypto protocols for the functionalities? :) This seems to be the option we are targetting when we show our comparisons and we say that we beat or match hand-crafted protocols}

@@

In this work, we develop and implement our framework \tool \nc{I still like EasyPC :)} for secure computation that achieves generality, performance and programmer productivity. The programmer writes a high level C-like program (instead of a circuit) to describe the function to be computed. Our compiler automatically generates an SMC protocol using a mix of Arithmetic and Boolean compute. Our compiler is general and can work with any secure implementation of a mix of arithmetic and boolean computations. In our work, we focus on semi-honest secure two-party computation. We build on ABY \cite{aby} that provides the suitable cryptographic back-end in this setting. We provide a formal type system and prove correctness and security of our compiler. We evaluate our system on various benchmarks such as logistic regression and convolutional neural network (CNN) for MNIST data \cite{minionn}, naive bayes, decision trees from \cite{shafindss}. Evaluations show that protocols generated by our compiler match the performance of hand-crafted protocols in most cases (see \sectionref{sec:eval}). \divya{Below, we will  give an overview of \tool and describe our contributions in more detail.}

@@

We give a formal {\em type system} for our language and prove useful properties. We prove that if a program type checks in our language then it would run correctly, e.g., there would not be any array index out of bounds error. The programmer writes a single code describing the inputs from each party and the function to be computed. Our compiler automatically generates separate executables for the server and the client that can be executed in the distributed setting. We prove the {\em correctness} for this compilation, i.e., the outputs obtained in the distributed execution are identical to the stand-alone execution by a trusted third party. We formally reduce the {\em security} of our system to the security of the cryptographic back-end. For details on formal language, correctness and security theorems see \sectionref{ld}.
\nc{Shall we have paragraph heads or someting to outline the different contributions? Above feels like one big story.}

Another issue in adoption of SMC is difficulty in scaling to large programs. 
%In general, SMC implementations struggle in scaling to large programssize of memory on a system limits the largest compute inside the SMC and hence,. 
The reason being all SMC implementations use a circuit-like representation as an intermediate representation. Hence, the largest compute that can be done securely is upper-bounded by the largest circuit that can fit in memory on a machine. \nc{Should we point out here that ABY itself has an explicit limit on circuit size and also give an example of a program that easily surpasses this bound? Also, hadnt ABY also said something about this? If so, we can mention this.}
To address this issue, we develop a technique called \emph{pipelining} that allows us to run aribitrarily large programs. At a high level, we break the original program into a sequence of small sub-programs and mask the intermediate outputs using secure secret sharing between the two parties. We appropriately append the share-reconstruction function to the beginning of the subsequent sub-program. Now, we execute each of these sub-programs sequentially in our framework. We provide details of pipelining and prove the correctness and security of this transformation in \sectionref{pipe}.
